---
title: "Introduction to rvisidata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to rvisidata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setup

```{r setup}
library(rvisidata)
```

You need to have VisiData installed. Please follow the official installation instructions [provided here](https://www.visidata.org/install/).

To verify visidata is installed correctly, `vd --version` should print out the installed version.

## Introduction to rvisidata

Use `rvisidata` with the `iris` dataset.

```{r vd-iris, eval=FALSE}
# This function calls an interactive VisiData session with the provided data frame.
# The session will block any further code execution until it's exited.
# The \dontrun{} is used here to prevent execution during vignette rendering and R CMD check.
#' \dontrun{
vd(iris)
#' }
```

## Limitations

Any changes to the data made in within VisiData is *not* stored or passed back to `R`. You can use VisiData solely to display and explore the data.
